\documentclass[letterpaper,10pt]{article}
\pagestyle{empty}
\usepackage{bookman}

\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{-0.5in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}

\newenvironment{narrowitemize}{
    \begin{list}{\textbullet{}}{%
        \setlength{\topsep}{0pt}%
        \setlength{\itemsep}{0pt}%
        \setlength{\parsep}{0pt}%
    }
}{\end{list}}

\begin{document}

\begin{center}
    {\Large Michael T Miller} \\
    \input{address1} \hspace{\parindent} \input{address2} \hspace{\parindent} \input{phone} \\
    \input{email}
    \rule[4pt]{\columnwidth}{0.5pt}
\end{center}

\noindent OBJECTIVE

\addtolength{\columnwidth}{-\parindent}

\parbox[t]{\columnwidth}{Electrical engineer seeking position in
digital signal processing, hardware driver design, operating systems,
or related fields.}

\bigskip

\noindent EDUCATION

\textbf{Georgia Institute of Technology}, Atlanta, GA\hfill{}Fall 1998
to Fall 2001

Bachelor of Science in Computer Engineering (with highest honors) -
December, 2001

Overall GPA: 3.97\hspace{\parindent}Major GPA: 4.00

\hspace{\parindent}Henry Ford II Scholar Award

\medskip

\textbf{University of Maryland}, College Park, MD\hfill{}Fall 1997 to
Spring 1998

\hspace{\parindent}Electrical Engineering Merit Scholarship;
President's Scholarship; Honors Program

\bigskip

\noindent PROJECT EXPERIENCE

\begin{narrowitemize}

    \item Designed simple processor with keyboard and VGA interface
          using VHDL and assembly-level software to implement game
          application on CPLD.

    \item Programmed PIC family of microcontrollers, working with
          digital and analog devices and peripherals.

    \item Designed simple computer architecture using VHDL and
          software to control mobile robot constructed around CPLD.

    \item Designed layout of 8-bit register, adder, and control unit
          using Cadence and Synopsis VLSI design tools.

\end{narrowitemize}

\bigskip

\noindent WORK EXPERIENCE

\textbf{H I Solutions}, Kennesaw, GA

Computer Engineering Intern\hfill{}Summer 2001

\begin{narrowitemize}

    \item Updated embedded firmware for compatibility with replacement
          hardware component.

    \item Created firmware and board design for replacement of
          existing network interface product.

    \item Made improvements in application-level and network-level
          software for handheld computer devices.

\end{narrowitemize}

\medskip

\textbf{Georgia Tech College of Computing}, Atlanta, GA

Teaching Assistant\hfill{}Fall 1999 to Fall 2001

\begin{narrowitemize}

    \item Taught recitation to 30-60 students, introduced new
          material, and reviewed information from lecture.

    \item Graded assignments and tests and answered questions to
          relieve the workload of professors.

    \item Provided weekly personal help and tutoring to each of 10-20
          students.

\end{narrowitemize}

\medskip

\textbf{SunTrust Service Corporation}, Atlanta, GA

Information Services Intern\hfill{}Summer 2000

\begin{narrowitemize}

    \item Supported and assisted with existing procedures for ordering
          and invoicing computer equipment.

    \item Created new database system for entering, updating, and
          reporting invoice information, eliminating redundancy and
          reducing time expenditure by 70\%.

    \item Created queries of inventory database to eliminate false
          records and improve tracking of equipment.

\end{narrowitemize}

\bigskip

\noindent SKILLS

\parbox[t]{\columnwidth}{Software/Programming: C, C++, Java, Perl,
Tcl; UNIX, GNU/Linux, MS DOS/Windows; MS Office; HTML, JavaScript,
CSS; MATLAB, Mathematica, MathCad; Altera, PSPICE, Cadence, Synopsis}

\bigskip

\noindent ACTIVITIES

\parbox[t]{\columnwidth}{Tau Beta Pi engineering honor society; Eta
Kappa Nu electrical engineering honor society; Institute of Electrical
and Electronics Engineers (IEEE); IEEE Computer Society; Association
for Computing Machinery (ACM)}

\end{document}
